Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels

### 2018-04-11 articles/formalism/sections/real_space_formalism.tex
moved the matrix notation later.

Using the definition of $\mathcal{E/B}$, the spin spherical harmonic decomposition of ${}_{\pm2}X$ and the identities given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are given by the following equations,
%
\beq \label{eq:pseudo}
\mathcal{E}(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) ~\,;~ \mathcal{B}(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) \,,
\eeq
%
where the harmonic coefficients $a^{E}_{\ell m}$  \& $a^{B}_{\ell m}$ are related to the harmonic coefficients of the spin-2 polarization field via the following equations,
%
\beq\label{eq:x2eb}
a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + {}_{-2}\tilde{X}_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - {}_{-2}\tilde{X}_{\ell m} \Big] \,.
\eeq
%
In the remainder of this article, we will work with the scalar $E$ and pseudo scalar $B$ fields as defined by the following equations, 
%
\beq \label{eq:realeb}
E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n}) ~\,;~ B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
\eeq
%
Note that these $E/B$ fields are merely filtered versions of $\mathcal{E}/\mathcal{B}$ as their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$. %We make this choice since the CMB spectra are more closely related to the fields E \& B.
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Matrix notation} \label{sec:mat_pol_intro}

We define transformations between different representations of the polarization field (i.e. from $Q,U$ to $_{\pm2} X$):
\beqrys
\bar T &=& \qutox_{2 \rm N_{\rm pix} \times 2 \rm N_{\rm pix}} ~~;~~ \bar T^{-1} = \frac{1}{2} \bar T^{\dagger} \,, \\
\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}} ~~;~~ \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,,
The sign conventions we have chosen match HEALPix.
Using the data vectors and the matrix operators defined above we can now express, in compact notation, the forward and inverse relations between different representations of the polarization data vectors as follows,
\begin{subequations} \label{eq:pol_data_relns}
  %Kevin's version
  \bar{X} &= \bar T  \bar{P}; &\qquad \bar{P} = \frac{1}{2} \bar T^{\dagger}  \bar{X} ; \\
  \tilde{X} &= \tilde T \tilde{S}; &\qquad \tilde{S} = \frac{1}{2}\tilde T^{\dagger} \tilde{X} \,.
  Meanwhile the spherical harmonic transforms are written as:
  \bar X &=  {{}_2\mathcal{Y}}  \tilde X; &\qquad \tilde X ={{}_2\mathcal{Y}}^{\dagger}  \bar X  ; \\
  \bar S &=  {{}_0\mathcal{Y}} \tilde S; &\qquad  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} \bar S \,.
% Aditya's version
%\beqry
%\bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
%\bar X &=&  {{}_2\mathcal{Y}} * \tilde X  ~~;~~ \tilde X ={{}_2\mathcal{Y}}^{\dagger} * \bar X  \,, \\
%\tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
%\bar S &=&  {{}_0\mathcal{Y}} * \tilde S ~~;~~  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} * \bar S \,.
%\tilde X &=&  {{}_2\mathcal{Y}}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
%\bar{S} &=& {{}_0\mathcal{Y}}*\tilde S ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\
%\bar{X} &=& \bar T * \bar{P} ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
%\bar{P} &=& \frac{1}{2} \bar T^{\dagger} * \bar{X} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,. \\
%\eeqry
Finally we introduce the operators that project harmonic space data vector to the $E$ or $B$ subspace,
\begin{subequations} \label{eq:har_eb_op}
\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E  \tilde S ,\\
\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B  \tilde S .
Note that these harmonic space matrices are idempotent ($\tilde O_E  \tilde O_E = \tilde O_E;  \tilde O_B  \tilde O_B= \tilde O_B$), orthogonal ($\tilde O_E  \tilde O_B = \mathbb{0}$), and sum to the identity matrix ($\tilde O_E + \tilde O_B = \mathbb{1}$).
%\begin{subequations} \label{eq:har_op_prop}
%\beqry
%\tilde O_E  \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B  \tilde O_B= \tilde O_B \,,\\
% \tilde O_E  \tilde O_B&=& \mathbb{0} \,, \label{eq:op_eb_ortho}\\ 
% \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
%\eeqry
%\end{subequations}
The above relations for these harmonic space operators are exactly valid.  In the following sections we aim to derive the real space analogues ($O_E,O_B$) of these harmonic space operators.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Real space operators} \label{sec:real_space_operators}
The vector-matrix notation introduced in  \sec{sec:mat_pol_intro} allows for concise book keeping of all the operations involved in the analysis of CMB polarization. In this section we use this notation to derive the real space operators which translate the Stokes vector \vp{}  to the vector of scalars \vs  and vice versa. This vector-matrix notation also allows us to simply derive real space operators for direct decomposition of the Stokes vector \vp{} in to a vector \vp{ E} that correspond to $E$-modes and another vector \vp{B} that corresponds to the $B$-modes of polarization, such that \vp{} = \vp{E} + \vp{B}, without ever evaluating the $E$ \& $B$ fields or their spherical harmonics. 
All the real space operators we derive are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere. Owing to this, we begin with a brief discussion on Euler angles and \revisit{present a visual method to think about them.}
\begin{figure}[!hbt]
\centering
\includegraphics[width=0.5\columnwidth]{euler.pdf}
\caption{This figure depicts the Euler angles in the z-y1-z2 convention. The cartesian coordinates shown in dark green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$. The blue coordinates at different locations are representative of the parallel transport along the geodesic connection the two locations $\hat{n}_q$ \& $\hat{n}_e$ on the sphere.}
\label{fig:euler_angles}
\end{figure}

@@

%--------------------------------------------------------
\subsection{Evaluating scalar fields $E$ \& $B$ from Stokes parameters $Q$ \& $U$}\label{sec:qu2eb}
In \sec{sec:pol-primer} we described the conventional procedure of computing the scalar fields E \& B from the Stokes parameters Q \& U. 
%To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 fields ${}_{\pm2} \bar X$, forming specific linear combinations of the resultant coefficients of expansion ${}_{\pm 2} \tilde X_{\ell m}$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields. 
In this section we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar fields $E$ \& $B$ on the sphere.  We use the vector-matrix notation introduced in \sec{sec:mat_pol_intro} to write down an operator equation relating the real space vector of scalars \vs to the Stokes polarization vector \vp{},
%
\beqrys
\bar{S} &=& {{}_0\mathcal{Y}} *\tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P}   \,, \\
&=&  \bar O *\bar{P} \,. \label{eq:qu2eb_op}
\eeqrys
%
The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators. This procedure is explicitly worked out in the following set of equations,
%
\beqrys
\bar{O} &=& \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T \,, \\
&=& -0.5 \yzmat{e} \qutoxd \ymatc{q} \qutox   \,, \\
&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_e ~{}_{2}Y^{T*}_q  +  {}_{0}Y_e~ {}_{-2}Y^{T*}_q) & {\rm i}  \sum ({}_{0}Y_e ~ {}_{2}Y^{T*}_q - {}_{0}Y_e ~{}_{-2}Y^{T*}_q)  \\  - {\rm i} \sum  ({}_{0}Y_e ~ {}_{2}Y^{T*}_q - {}_{0}Y_e~ {}_{-2}Y^{T*}_q) & \sum ({}_{0}Y_e~ {}_{2}Y^{T*}_q + {}_{0}Y_e ~{}_{-2}Y^{T*}_q)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
\eeqrys
%
where the symbol ${}_{0}Y_e$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_e \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_e)$, the symbol ${}_{\pm 2}Y^{T*}_q$ is used to denote the transposed conjugated matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_q} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_q)$ and the summation is over the multipole indices $\ell,m$. Note that here we purposefully introduce the notation of the index ``e'' to denote the location where the scalar fields are being evaluated and the index ``q'' to denote the location from which  the Stokes parameters are being accessed. Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following identity holds true,
%
\beq
 \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{+2}Y^*_{\ell m}(\hat{n}_q)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{-2}Y^*_{\ell m}(\hat{n}_q) \,,
 \eeq
 %
where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}. Note that the operator $\bar{O}$ is real as one expects, since each sub-matrix in \eq{eq:qu2eb_ker_1} is formed by summing a complex number and its conjugate.

>>>>

Using the definition of $\mathcal{E/B}$, the spin spherical harmonic decomposition of ${}_{\pm2}X$ and the identities given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are given by the following equations,
%
\beq \label{eq:pseudo}
\mathcal{E}(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) ~\,;~ \mathcal{B}(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) \,,
\eeq
%
where the harmonic coefficients $a^{E}_{\ell m}$  \& $a^{B}_{\ell m}$ are related to the harmonic coefficients of the spin-2 polarization field via the following equations,
%
\beq\label{eq:x2eb}
a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + {}_{-2}\tilde{X}_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - {}_{-2}\tilde{X}_{\ell m} \Big] \,.
\eeq
%
In the remainder of this article, we will work with the scalar $E$ and pseudo scalar $B$ fields as defined by the following equations, 
%
\beq \label{eq:realeb}
E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n}) ~\,;~ B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
\eeq
%
Note that these $E/B$ fields are merely filtered versions of $\mathcal{E}/\mathcal{B}$ as their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$. %We make this choice since the CMB spectra are more closely related to the fields E \& B.
%--------------------------------------------------------
%--------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Real space operators} \label{sec:real_space_operators}
The vector-matrix notation introduced in  \sec{sec:mat_pol_intro} allows for concise book keeping of all the operations involved in the analysis of CMB polarization. In this section we use this notation to derive the real space operators which translate the Stokes vector \vp{}  to the vector of scalars \vs  and vice versa. This vector-matrix notation also allows us to simply derive real space operators for direct decomposition of the Stokes vector \vp{} in to a vector \vp{ E} that correspond to $E$-modes and another vector \vp{B} that corresponds to the $B$-modes of polarization, such that \vp{} = \vp{E} + \vp{B}, without ever evaluating the $E$ \& $B$ fields or their spherical harmonics. 
All the real space operators we derive are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere. Owing to this, we begin with a brief discussion on Euler angles and \revisit{present a visual method to think about them.}
%
\begin{figure}[!hbt]
\centering
\includegraphics[width=0.5\columnwidth]{euler.pdf}
\caption{This figure depicts the Euler angles in the z-y1-z2 convention. The cartesian coordinates shown in dark green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$. The blue coordinates at different locations are representative of the parallel transport along the geodesic connection the two locations $\hat{n}_q$ \& $\hat{n}_e$ on the sphere.}
\label{fig:euler_angles}
\end{figure}
%

@@

%--------------------------------------------------------
\subsection{Matrix notation} \label{sec:mat_pol_intro}

We define transformations between different representations of the polarization field (i.e. from $Q,U$ to $_{\pm2} X$):
%
\beqrys
\bar T &=& \qutox_{2 \rm N_{\rm pix} \times 2 \rm N_{\rm pix}} ~~;~~ \bar T^{-1} = \frac{1}{2} \bar T^{\dagger} \,, \\
\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}} ~~;~~ \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,,
\eeqrys
%
The sign conventions we have chosen match HEALPix.
Using the data vectors and the matrix operators defined above we can now express, in compact notation, the forward and inverse relations between different representations of the polarization data vectors as follows,
%
\begin{subequations} \label{eq:pol_data_relns}
  %Kevin's version
  \beqry
  \bar{X} &= \bar T  \bar{P}; &\qquad \bar{P} = \frac{1}{2} \bar T^{\dagger}  \bar{X} ; \\
  \tilde{X} &= \tilde T \tilde{S}; &\qquad \tilde{S} = \frac{1}{2}\tilde T^{\dagger} \tilde{X} \,.
  \eeqry
  Meanwhile the spherical harmonic transforms are written as:
  \beqry
  \bar X &=  {{}_2\mathcal{Y}}  \tilde X; &\qquad \tilde X ={{}_2\mathcal{Y}}^{\dagger}  \bar X  ; \\
  \bar S &=  {{}_0\mathcal{Y}} \tilde S; &\qquad  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} \bar S \,.
  \eeqry
% Aditya's version
%\beqry
%\bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
%\bar X &=&  {{}_2\mathcal{Y}} * \tilde X  ~~;~~ \tilde X ={{}_2\mathcal{Y}}^{\dagger} * \bar X  \,, \\
%\tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
%\bar S &=&  {{}_0\mathcal{Y}} * \tilde S ~~;~~  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} * \bar S \,.
%\tilde X &=&  {{}_2\mathcal{Y}}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
%\bar{S} &=& {{}_0\mathcal{Y}}*\tilde S ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\
%\bar{X} &=& \bar T * \bar{P} ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
%\bar{P} &=& \frac{1}{2} \bar T^{\dagger} * \bar{X} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,. \\
%\eeqry
\end{subequations}
%
Finally we introduce the operators that project harmonic space data vector to the $E$ or $B$ subspace,
%
\begin{subequations} \label{eq:har_eb_op}
\beqry
\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E  \tilde S ,\\
\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B  \tilde S .
\eeqry
\end{subequations}
%
Note that these harmonic space matrices are idempotent ($\tilde O_E  \tilde O_E = \tilde O_E;  \tilde O_B  \tilde O_B= \tilde O_B$), orthogonal ($\tilde O_E  \tilde O_B = \mathbb{0}$), and sum to the identity matrix ($\tilde O_E + \tilde O_B = \mathbb{1}$).
%
%\begin{subequations} \label{eq:har_op_prop}
%\beqry
%\tilde O_E  \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B  \tilde O_B= \tilde O_B \,,\\
% \tilde O_E  \tilde O_B&=& \mathbb{0} \,, \label{eq:op_eb_ortho}\\ 
% \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
%\eeqry
%\end{subequations}
%
The above relations for these harmonic space operators are exactly valid.  In the following sections we aim to derive the real space analogues ($O_E,O_B$) of these harmonic space operators.

\subsection{Evaluating scalar fields $E$ \& $B$ from Stokes parameters $Q$ \& $U$}\label{sec:qu2eb}
In \sec{sec:pol-primer} we described the conventional procedure of computing the scalar fields E \& B from the Stokes parameters Q \& U. 
%To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 fields ${}_{\pm2} \bar X$, forming specific linear combinations of the resultant coefficients of expansion ${}_{\pm 2} \tilde X_{\ell m}$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields. 
In this section we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar fields $E$ \& $B$ on the sphere.  We use the vector-matrix notation introduced in \sec{sec:mat_pol_intro} to write down an operator equation relating the real space vector of scalars \vs to the Stokes polarization vector \vp{},
%
\beqrys
\bar{S} &=& {{}_0\mathcal{Y}} *\tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P}   \,, \\
&=&  \bar O *\bar{P} \,. \label{eq:qu2eb_op}
\eeqrys
%
The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators. This procedure is explicitly worked out in the following set of equations,
%
\beqrys
\bar{O} &=& \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T \,, \\
&=& -0.5 \yzmat{e} \qutoxd \ymatc{q} \qutox   \,, \\
&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_e ~{}_{2}Y^{T*}_q  +  {}_{0}Y_e~ {}_{-2}Y^{T*}_q) & {\rm i}  \sum ({}_{0}Y_e ~ {}_{2}Y^{T*}_q - {}_{0}Y_e ~{}_{-2}Y^{T*}_q)  \\  - {\rm i} \sum  ({}_{0}Y_e ~ {}_{2}Y^{T*}_q - {}_{0}Y_e~ {}_{-2}Y^{T*}_q) & \sum ({}_{0}Y_e~ {}_{2}Y^{T*}_q + {}_{0}Y_e ~{}_{-2}Y^{T*}_q)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
\eeqrys
%
where the symbol ${}_{0}Y_e$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_e \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_e)$, the symbol ${}_{\pm 2}Y^{T*}_q$ is used to denote the transposed conjugated matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_q} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_q)$ and the summation is over the multipole indices $\ell,m$. Note that here we purposefully introduce the notation of the index ``e'' to denote the location where the scalar fields are being evaluated and the index ``q'' to denote the location from which  the Stokes parameters are being accessed. Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following identity holds true,
%
\beq
 \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{+2}Y^*_{\ell m}(\hat{n}_q)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{-2}Y^*_{\ell m}(\hat{n}_q) \,,
 \eeq
 %
where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}. Note that the operator $\bar{O}$ is real as one expects, since each sub-matrix in \eq{eq:qu2eb_ker_1} is formed by summing a complex number and its conjugate.
